Persistent homology for functionals

### 2023-05-16 sec/caps.tex
Fix broken references
lem:sublevel_set_homotopy
to
thm:sublevel_set_homotopy.

\section{Regular values and cap numbers} \label{s:caps}
We will now discuss the equivalence of our definition of cap numbers and the one used by Morse.
Futhermore, we provide a proof of \cref{lem:sublevel_set_homotopy} establishing a homotopy equivalence of sublevel sets at a regular value.
As a starting point, we observe that the basic use of \cref{lem:sublevel_set_homotopy} is to show that if $t$ is an endpoint of a feature in the persistence diagram associated to our function $F$, i.e., if $c(t) > 0$, then there must be a homotopically critical point with value $t$.
To achieve this, we assume that $F$ is weakly upper-reducible and its sublevel set filtration is compact.
A very similar statement appears in \cite[Theorem 8.1]{Morse.1938}, which says that if $t$ is a \emph{cap limit}, then there must be a homotopically critical point with value $t$.
There are two slight differences to our approach:
First, in \cite[Theorem 8.1]{Morse.1938} it is assumed that $F$ is not only weakly upper-reducible but upper-reducible.
Second, $t$ is not required to satisfy $c(t) > 0$, but required to be a \emph{cap limit}, meaning that $\colim_{s: s < t} \CH(F_{\leq t}, F_{\leq s}) \neq 0$ \cite[p.~12]{Morse.1938}.
Regarding the second point, it turns out that the two requirements are equivalent.

@@

We now discuss the difference between our approach and the one from \cite[Theorem 8.1]{Morse.1938} concerning the assumption of upper-reducibility.
We will show that our weakened assumptions are sufficient for the conclusion, giving an outline of the arguments leading up to \cite[Theorem 8.1]{Morse.1938} invoking only weak upper-reducibility.
As mentioned previously, similar considerations can be found in \cite[Remark II.6.3]{Struwe.1988} (although the role of weak upper-reducibility is not addressed there). 
\begin{proof}[Proof of \cref{lem:sublevel_set_homotopy}]
	Let $t \in \R$ be a regular value of $F$.
	For each $p \in F_{\leq t}$ we can find a number $\delta_{p} > 0$ and a continuous map $\varphi_{p} \colon B_{\delta_{p}}(p) \times [0,1] \to M$, where $B_{\delta_{p}}(p)$ is the open metric ball around $p$ in $F_{\leq t}$ with radius $\delta_{p}$, such that
	\begin{enumerate}[label={(\arabic*)}]
		\item \label{item:id} $\varphi_{p}(\cdot,0) = \operatorname{id}$,
		\item \label{item:epsilon} for all compact $V \subseteq B_{\delta_{p}}(p)$ there exists $\epsilon(p,V) > 0$ with
		\begin{enumerate}[label={(\alph*)}]
			%\item $F(\varphi_{p}(x,r))$ is non-increasing in $r$ for all $x \in B_{\delta_{p}}(p)$, and
			\item \label{item:s_below_s} $\varphi_{p}(V \cap F_{\leq s}\times [0,1]) \subseteq F_{\leq s}$ for all $s \in [t - \epsilon(p,V), t]$,
			\item \label{item:contracting} $\varphi_{p}(V,1) \subseteq F_{\leq t - \epsilon(p,V)}$, and
			\item \label{item:displacement} there exists a displacement function for $\varphi_{p}$ and $F$ on $V \cap F_{\geq t - \epsilon(p,V)}$.
		\end{enumerate}
	\end{enumerate}
	For $p$ with $F(p) < t$ the existence of such $\delta_{p}$ and $\varphi_{p}$ is guaranteed by the assumption that $F$ is weakly upper-reducible.
	For $p$ with $F(p) = t$ it follows from the assumption that $t$ is a regular value and hence $p$ is homotopically regular, by the following argument.

>>>>

\section{Regular values and cap numbers} \label{s:caps}
We will now discuss the equivalence of our definition of cap numbers and the one used by Morse.
Futhermore, we provide a proof of \cref{thm:sublevel_set_homotopy} establishing a homotopy equivalence of sublevel sets at a regular value.
As a starting point, we observe that the basic use of \cref{thm:sublevel_set_homotopy} is to show that if $t$ is an endpoint of a feature in the persistence diagram associated to our function $F$, i.e., if $c(t) > 0$, then there must be a homotopically critical point with value $t$.
To achieve this, we assume that $F$ is weakly upper-reducible and its sublevel set filtration is compact.
A very similar statement appears in \cite[Theorem 8.1]{Morse.1938}, which says that if $t$ is a \emph{cap limit}, then there must be a homotopically critical point with value $t$.
There are two slight differences to our approach:
First, in \cite[Theorem 8.1]{Morse.1938} it is assumed that $F$ is not only weakly upper-reducible but upper-reducible.
Second, $t$ is not required to satisfy $c(t) > 0$, but required to be a \emph{cap limit}, meaning that $\colim_{s: s < t} \CH(F_{\leq t}, F_{\leq s}) \neq 0$ \cite[p.~12]{Morse.1938}.
Regarding the second point, it turns out that the two requirements are equivalent.

@@

We now discuss the difference between our approach and the one from \cite[Theorem 8.1]{Morse.1938} concerning the assumption of upper-reducibility.
We will show that our weakened assumptions are sufficient for the conclusion, giving an outline of the arguments leading up to \cite[Theorem 8.1]{Morse.1938} invoking only weak upper-reducibility.
As mentioned previously, similar considerations can be found in \cite[Remark II.6.3]{Struwe.1988} (although the role of weak upper-reducibility is not addressed there).
\begin{proof}[Proof of \cref{thm:sublevel_set_homotopy}]
	Let $t \in \R$ be a regular value of $F$.
	For each $p \in F_{\leq t}$ we can find a number $\delta_{p} > 0$ and a continuous map $\varphi_{p} \colon B_{\delta_{p}}(p) \times [0,1] \to M$, where $B_{\delta_{p}}(p)$ is the open metric ball around $p$ in $F_{\leq t}$ with radius $\delta_{p}$, such that
	\begin{enumerate}[label={(\arabic*)}]
		\item \label{item:id} $\varphi_{p}(\cdot,0) = \operatorname{id}$,
		\item \label{item:epsilon} for all compact $V \subseteq B_{\delta_{p}}(p)$ there exists $\epsilon(p,V) > 0$ with
		\begin{enumerate}[label={(\alph*)}]
			%\item $F(\varphi_{p}(x,r))$ is non-increasing in $r$ for all $x \in B_{\delta_{p}}(p)$, and
			\item \label{item:s_below_s} $\varphi_{p}(V \cap F_{\leq s}\times [0,1]) \subseteq F_{\leq s}$ for all $s \in [t - \epsilon(p,V), t]$,
			\item \label{item:contracting} $\varphi_{p}(V,1) \subseteq F_{\leq t - \epsilon(p,V)}$, and
			\item \label{item:displacement} there exists a displacement function for $\varphi_{p}$ and $F$ on $V \cap F_{\geq t - \epsilon(p,V)}$.
		\end{enumerate}
	\end{enumerate}
	For $p$ with $F(p) < t$ the existence of such $\delta_{p}$ and $\varphi_{p}$ is guaranteed by the assumption that $F$ is weakly upper-reducible.
	For $p$ with $F(p) = t$ it follows from the assumption that $t$ is a regular value and hence $p$ is homotopically regular, by the following argument.
